Poseidon Adventure

### 2020-06-05 NOBAcod.Rmd
update with new interpolated wtage

#library(here) now above
library(tidyverse)
library(atlantisom)

@@

library(ggthemes)
omlist_ss <- NOBAom_cod
source(here("config/omdimensions.R"))

@@

#### Survey weight at age (annual ages) pending new function
```{r plot-annwtage}

@@

>>>>

#library(here) now above
library(tidyverse)
library(atlantisom)
library(ggthemes)

@@

omlist_ss <- NOBAom_cod
source(here("config/omdimensions.R"))

@@

#### Survey iterpolated weight at age (annual ages) 
```{r plot-annwtage}

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "survObsFullWtAtAge.rds")))
wtage <- wtage[[1]] #this still has second list component, diagnostic plot
wtage <- wtage[[1]]

wageplot + facet_wrap(c("species"), scales="free_y")

@@

#### Fishery iterpolated weight at age (annual ages) 
```{r plot-fishannwtage}

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullWtAtAge.rds")))
wtage <- wtage[[1]] #this still has second list component, diagnostic plot
wtage <- wtage[[1]]

wageplot + facet_wrap(c("species"), scales="free_y")

### 2020-06-05 docs/index.Rmd
moderately successful wt at age interpolation
correct spelling
update index
update with new interpolated wtage

### Apply wrapper to Norwegian Barents cod, March 2020

<a href="https://sgaichas.github.io/poseidon-dev/NOBAcod.html" target="_blank">Apply and extend wrappers to get full age structure, updated June 1, 2020</a>

>>>>

### Full age structured dataset for Norwegian Barents cod, March-June 2020

<a href="https://sgaichas.github.io/poseidon-dev/NOBAcod.html" target="_blank">Apply and extend wrappers to get full age structure, updated June 5, 2020</a>

<a href="https://sgaichas.github.io/poseidon-dev/InterpolateWeightAtAge.html" target="_blank">Interpolate to get average weight at true age, June 5, 2020</a>

Also bug fixed config files for multispecies dataset. Interpolate wtage includes data generation for NOBA cod (max age 20), redfish (max age 40), and capelin (max age 5).
